Fully Automatic Loop-free Program Synthesis by Bounded Model Checking

### 2013-10-11 paper/paper.tex
Future work

\paragraph{Future Work}
Another benefit of using \newC as our logic is that it would be easy to
automatically extract specifications from C programs, which would be
useful in the context of superoptimisation.  This is because \newC is
a relatively large fragment of C, so we anticipate that many interesting
sections of real code will already be~\newC.

>>>>

\paragraph{Future Work}
It may be possible to extend the language $\mathcal{L}$ with constructs such as branching and limited
looping while still retaining decidability, which would be an interesting direction to pursue.
Since our specification language is a subset of C, interfacing {\sc kalashnikov} with
other analysis tools should not be too difficult.  Various problems such as ranking function synthesis,
loop invariant generation and loop summarisation can be phrased as program synthesis problems,
and we would like to investigate the possiblities of applying {\sc kalashnikov} to these domains.
